Supporting Information for "Geometric models overestimate lake depth due to imperfect slope measurement"

### 2020-11-24 manuscript/si_template_2019.tex
add response figure and table placeholders

@@

@@

\begin{table}
\caption{Summary of lake characteristics for the present study (and for lakes in the contiguous United States). Predictor variables for computing random forest offsets (Equation 2) are printed in bold face. Dashes (-) indicate an identical sample size among this study and that of the contiguous United States.} \label{tableS1}
\centering
\setlength\tabcolsep{1.5pt} % default value: 6pt
\begin{tabular}{lllll}
  \hline
  Variable & Median & Q25 & Q75 & n\\
  \hline
  Max depth (m) & 8.2 (7) & 4.6 (3.7) & 14 (12) & 4850 (17700)\\
  \textbf{Elevation (m)} & 300 (340) & 180 (210) & 400 (460) & 4850 (17700)\\
  \textbf{Area (ha)} & 55 (33) & 21 (11) & 140 (100) & 4850 (17700)\\
  \textbf{Island area (ha)} & 0 (0) & 0 (0) & 0.18 (0.076) & 4850 (17700)\\
  \textbf{Perimeter (m)} & 4400 (3500) & 2500 (1800) & 8100 (7300) & 4850 (17700)\\
  \textbf{Shoreline development} & 1.7 (1.7) & 1.4 (1.4) & 2.1 (2.2) & 4850 (17700)\\
  \textbf{Watershed-lake ratio} & 7.8 (10) & 3.9 (4.4) & 17 (28) & 4850 (17700)\\
  Distance to deepest point (m) & 180 (-) & 110 (-) & 290 (-) & 4850 (-)\\
  Distance to lake center (m) & 240 (-) & 160 (-) & 380 (-) & 4850 (-)\\
  In-lake slope (m/m) & 0.046 (-) & 0.024 (-) & 0.079 (-) & 4850 (-)\\
  Nearshore land slope (m/m) & 0.077 (-) & 0.051 (-) & 0.11 (-) & 4850 (-)\\
  \hline
  \end{tabular}
\end{table}

>>>>

\begin{figure}
      \begin{center}
        \includegraphics[width=\textwidth,keepaspectratio]{../figures/01_slope_compare-1}
      \end{center}
      \caption{Sensitivity analysis regarding different slope calculation methods.}\label{figS1}
    \end{figure}
\clearpage

@@

\begin{figure}
      \begin{center}
        \includegraphics[width=0.75\textwidth,keepaspectratio]{../figures/slope_by_area_depth-1}
      \end{center}
      \caption{Compare the mean lake slopes in concave and convex lakes of the same size and max depth.}\label{figS1}
    \end{figure}
\clearpage

@@

% source at tables/01_predictors.Rmd
\begin{table}
\caption{Summary of lake characteristics for the present study (and for lakes in the contiguous United States). Predictor variables for computing random forest offsets (Equation 2) are printed in bold face. Dashes (-) indicate an identical sample size among this study and that of the contiguous United States.} \label{tableS1}
\centering
\setlength\tabcolsep{1.5pt} % default value: 6pt

\begin{tabular}{lllll}
\hline
Variable & Median & Q25 & Q75 & n\\
\hline
\textbf{Area (ha)} & 55 (33) & 21 (11) & 140 (100) & 4820 (17700)\\
\textbf{Island area (ha)} & 0 (0) & 0 (0) & 0.18 (0.076) & 4820 (17700)\\
- & 1500 (1100) & 880 (640) & 2500 (2200) & 4820 (17700)\\
- & 91 (88) & 41 (40) & 140 (140) & 4820 (17700)\\
- & 710 (560) & 430 (320) & 1200 (1000) & 4820 (17700)\\
- & 380 (290) & 230 (170) & 610 (500) & 4820 (17700)\\
- & 0 (0) & 0 (0) & 58 (25) & 4820 (17700)\\
- & 0 (0) & 0 (0) & 3 (3) & 4820 (17700)\\
- & 0 (0) & 0 (0) & 1 (1) & 4820 (17700)\\
- & 26000 (27000) & 23000 (23000) & 27000 (38000) & 4820 (17700)\\
\textbf{Deepest point distance (m)} & 180 (-) & 110 (-) & 290 (-) & 4820 (-)\\
\textbf{Visual center distance (m)} & 240 (-) & 160 (-) & 390 (-) & 4820 (-)\\
- & 0.046 (-) & 0.024 (-) & 0.079 (-) & 4820 (-)\\

- & 0.062 (-) & 0.029 (-) & 0.14 (-) & 4800 (-)\\

- & 0.077 (-) & 0.051 (-) & 0.11 (-) & 4820 (-)\\

- & 0.077 (-) & 0.038 (-) & 0.13 (-) & 4590 (-)\\

- & 0.077 (-) & 0.037 (-) & 0.13 (-) & 4540 (-)\\
\hline
\end{tabular}
\end{table}

\begin{table}
\caption{Show model metrics for sensitivity analysis. Describe how each different metric was calculated.} \label{tableS2}
\centering
\setlength\tabcolsep{1.5pt} % default value: 6pt

\begin{tabular}{lllll}
\hline
Variable & Median & Q25 & Q75 & n\\
\hline
- & 0.077 (-) & 0.037 (-) & 0.13 (-) & 4540 (-)\\
\hline
\end{tabular}
\end{table}
